Codebook created on 2023-11-06 at 2023-11-06 15:00:38.16236

### 2023-11-06 Data/IntermediateData/codebook_coded_data_original_shortened.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:41.370241"
output: github_document
---

@@

## Dataset description
The data contains 80 cases and 91 variables.

@@

```{r}
summaries <- read.csv("codebook_coded_data_original.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:43.074438"
output: github_document
---

@@

## Dataset description
The data contains 77 cases and 91 variables.

@@

```{r}
summaries <- read.csv("codebook_coded_data_original_shortened.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_coded_data_replications.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:43.074438"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_coded_data_original_shortened.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:38.034183"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_coded_data_replications.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_1.10_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:01:38.034183"
output: github_document
---

@@

## Dataset description
The data contains 77 cases and 91 variables.

@@

```{r}
summaries <- read.csv("codebook_coded_data_replications.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:48.763887"
output: github_document
---

@@

## Dataset description
The data contains 6344 cases and 9 variables.

@@

```{r}
summaries <- read.csv("codebook_data_1.10_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_1.11_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:48.763887"
output: github_document
---

@@

## Dataset description
The data contains 6344 cases and 9 variables.

@@

```{r}
summaries <- read.csv("codebook_data_1.10_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:53.640585"
output: github_document
---

@@

## Dataset description
The data contains 6344 cases and 5 variables.

@@

```{r}
summaries <- read.csv("codebook_data_1.11_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_1.12.3.1_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:53.640585"
output: github_document
---

@@

## Dataset description
The data contains 6344 cases and 5 variables.

@@

```{r}
summaries <- read.csv("codebook_data_1.11_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:55.690988"
output: github_document
---

@@

## Dataset description
The data contains 6344 cases and 7 variables.

@@

```{r}
summaries <- read.csv("codebook_data_1.12.3.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_1.12.3.2_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:55.690988"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_1.12.3.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:59.490912"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_1.12.3.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_1.3_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:48.763887"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_1.10_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:47.592344"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_1.3_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_2.10.1_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 14:59:47.592344"
output: github_document
---

@@

## Dataset description
The data contains 6344 cases and 9 variables.

@@

```{r}
summaries <- read.csv("codebook_data_1.3_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:03.000904"
output: github_document
---

@@

## Dataset description
The data contains 6234 cases and 7 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.10.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_2.12.1_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:03.000904"
output: github_document
---

@@

## Dataset description
The data contains 6234 cases and 7 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.10.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:04.937275"
output: github_document
---

@@

## Dataset description
The data contains 6905 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.12.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_2.12.2_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:04.937275"
output: github_document
---

@@

## Dataset description
The data contains 6905 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.12.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:08.026037"
output: github_document
---

@@

## Dataset description
The data contains 6905 cases and 11 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.12.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_2.12.3_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:08.026037"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_2.12.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:10.467392"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_2.12.3_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_2.15_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:10.467392"
output: github_document
---

@@

## Dataset description
The data contains 6905 cases and 11 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.12.3_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:11.960889"
output: github_document
---

@@

## Dataset description
The data contains 7890 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.15_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_2.20_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:11.960889"
output: github_document
---

@@

## Dataset description
The data contains 7890 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.15_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:15.161093"
output: github_document
---

@@

## Dataset description
The data contains 7396 cases and 21 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.20_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_2.23_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:15.161093"
output: github_document
---

@@

## Dataset description
The data contains 7396 cases and 21 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.20_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:17.859936"
output: github_document
---

@@

## Dataset description
The data contains 7001 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.23_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_3.2.1.1_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:17.859936"
output: github_document
---

@@

## Dataset description
The data contains 7001 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_2.23_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:19.053091"
output: github_document
---

@@

## Dataset description
The data contains 1620 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.2.1.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_3.2.1.2_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:19.053091"
output: github_document
---

@@

## Dataset description
The data contains 1620 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.2.1.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:21.765723"
output: github_document
---

@@

## Dataset description
The data contains 1666 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.2.1.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_3.7.1_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:21.765723"
output: github_document
---

@@

## Dataset description
The data contains 1666 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.2.1.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:24.954882"
output: github_document
---

@@

## Dataset description
The data contains 2429 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.7.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_3.7.2_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:24.954882"
output: github_document
---

@@

## Dataset description
The data contains 2429 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.7.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:26.441641"
output: github_document
---

@@

## Dataset description
The data contains 3178 cases and 7 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.7.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_3.8.2_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:26.441641"
output: github_document
---

@@

## Dataset description
The data contains 3178 cases and 7 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.7.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:29.432437"
output: github_document
---

@@

## Dataset description
The data contains 3208 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.8.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_5.1.1_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:29.432437"
output: github_document
---

@@

## Dataset description
The data contains 3208 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_data_3.8.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:31.816934"
output: github_document
---

@@

## Dataset description
The data contains 471 cases and 22 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.1.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_5.4_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:31.816934"
output: github_document
---

@@

## Dataset description
The data contains 471 cases and 22 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.1.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:33.922557"
output: github_document
---

@@

## Dataset description
The data contains 556 cases and 25 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.4_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_5.7_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:33.922557"
output: github_document
---

@@

## Dataset description
The data contains 556 cases and 25 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.4_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:36.662196"
output: github_document
---

@@

## Dataset description
The data contains 5476 cases and 11 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.7_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-06 Data/IntermediateData/codebook_data_5.9.1_clean.Rmd
added the data cleaning functions

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:36.662196"
output: github_document
---

@@

## Dataset description
The data contains 5476 cases and 11 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.7_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:38.16236"
output: github_document
---

@@

## Dataset description
The data contains 341 cases and 8 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.9.1_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```
